Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-10 doc/paper-lcr.tex
marginalisation over \kappah is not a convolution!

The PDF $\Pr(\kappah|\{\Mstarobsk,z_k\})$ will, in general, be broad (due to
the uncertainties involved in halo mass estimation). It will also be shifted
towards high values of convergence, due to the FRW approximation described
above. What we really want is an inference of $\Pr(\kappa|\{\Mstarobsk,z_k\})$
instead. We can obtain this by considering the expansion:
\begin{equation}
\Pr(\kappa|\{\Mstarobsk,z_k\}) = \int d\kappah 
   \Pr(\kappa|\kappah) \Pr(\kappah|\{\Mstarobsk,z_k\})
\label{eq:kappaconv}   
\end{equation}
The first term in the integrand relates the summed  convergence due to model
halos, $\kappah$, to the true summed convergence, $\kappa$.  In the Millenium
Simulation catalogs, we can compute a single value of $\kappah$ for each
selected line of sight from the true halo mass and redshift (and our same
assumptions of halo profile and shape), and tabulate the two-dimensional PDF
$\Pr(\kappa|\kappah)$ as a sequence of one-dimensional PDFs for $\kappa$ in a
bin at fixed $\kappah$. Note that this PDF captures the ``intrinsic scatter''
of $\kappah$ due to our assumptions about the clumpiness of mass in the
Universe; the integral is the convolution of this distribution with that
arising from our observational uncertainties.

>>>>

The PDF $\Pr(\kappah|\{\Mstarobsk,z_k\})$ will, in general, be broad (due to
the uncertainties involved in halo mass estimation). It will also be shifted
towards high values of convergence, due to the FRW approximation described
above. What we really want is an inference of $\Pr(\kappa|\{\Mstarobsk,z_k\})$
instead. We can obtain this by considering the expansion:
\begin{equation}
\Pr(\kappa|\{\Mstarobsk,z_k\}) = \int d\kappah 
   \Pr(\kappa|\kappah) \Pr(\kappah|\{\Mstarobsk,z_k\})
\label{eq:kappaconv}   
\end{equation}
The first term in the integrand relates the summed  convergence due to model
halos, $\kappah$, to the true summed convergence, $\kappa$.  In the Millenium
Simulation catalogs, we can compute a single value of $\kappah$ for each
selected line of sight from the true halo mass and redshift (and our same
assumptions of halo profile and shape), and tabulate the two-dimensional PDF
$\Pr(\kappa|\kappah)$ as a sequence of one-dimensional PDFs for $\kappa$ in a
bin at fixed $\kappah$. Note that this PDF captures the ``intrinsic scatter''
of $\kappah$ due to our assumptions about the clumpiness of mass in the
Universe; the integral combines these uncertainties with those
arising from the measurement of $\Mstarobs$ and~$z$.
